Solving a probabilistic planning problem by presenting a history in the field of probabilistic planning

### 2014-04-13 FinalPaper/paper.tex
More conclusion

To choose an appropriate planner for the UAV domain, we have discussed other
existing benchmark domains used in the IPPC.

>>>>

To choose an appropriate planner for the UAV domain, we have discussed other
existing benchmark domains used in the IPPC\. By looking closely at the domains
we identified some issues with the domains, to make it more difficult for
FF-Replan (in the case of the \textsc{Traffic} domain), of how to make a domain
easier for a replanner in the \textsc{Navigation} domain. The UAV domain seems
to have resemblances of the \textsc{Navigation} domain and the
\textsc{SysAdmin} domain.

Finally we described to other relevant planners RFF and PROST\. RFF is a
planner similar to FF-Replan, but instead works off-line and generates
policies. PROST is a UTC based probabilistic planner that outperformed
\textsc{Gourmand}'s predecessor \textsc{Glutton}.
